---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rsrm

<!-- badges: start -->
<!-- badges: end -->

## Description
The goal of rsrm is to generate the distribution of Restriction Sites on given DNA sequence and also construct the Restriction Map with given single and double digests reaction result.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
require("devtools")
install_github("LoadingBFX/rsrm", build_vignettes = TRUE)
library("rsrm")
```

To run the shinyApp:
``` r
<ShinyAppName>()
```
## Overview

``` r
browseVignettes("rsrm")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rsrm)
## basic example code
```

## Contributions
``` r
library("rsrm")
lsf.str("package:rsrm")
```

## References

## Acknowledgements
This package was developed as part of an assessment for 2019 BCB410H: Applied Bioinformatics, University of Toronto, Toronto, CANADA.
