---
title: "Introduction_rsrm"
author: "Fanxing Bu"
date: "`r format(Sys.time(), '%d %b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_rsrm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rsrm)
```

# Introduction

**rsrm** is a contributed R package for restriction sites mapping for known DNA sequence and construct the restriction map for unkown DNA sequence with given single and double digests reaction result.

# Restriction Sites Mapping for Known DNA Sequence

```{r fig.width=7,fig.height=6}
    seq1 <- 'GGCAGATTCCCCCTAACGTCGGACCCGCCCGCACCATGGTCAGGCATGCCCCTCCTCATCGCTGGGCACAGCCCAGAGGGT
    ATAAACAGTGCTGGAGGCTGGCGGGGCAGGCCAGCTGAGTCCTGAGCAGCAGCCCAGCGCAGCCACCGAGACACC
    ATGAGAGCCCTCACACTCCTCGCCCTATTGGCCCTGGCCGCACTTTGCATCGCTGGCCAGGCAGGTGAGTGCCCC'
    name1 <- 'example DNA Sequence'
    seq2 <- 'ACGTCG'
    name2 <- 'Target'
    result <- findre(name1, seq1, name2, seq2)
    result
```

# Construct Restriction Map for Unkown DNA Sequence

```{r fig.width=7,fig.height=6}
frag1 <- c(100)
frag2 <- c(50, 25, 20, 5)
dou_dig <- c(25, 25, 25, 20, 5)
enz1 <- 'enz1'
enz2 <- 'enz2'
result <- rsmap(enz1, frag1, enz2, frag2, dou_dig)
result
```

# References
Scrucca L., Fop M., Murphy T. B. and Raftery A. E. (2016) mclust 5: clustering, classification and density estimation using Gaussian finite mixture models The R Journal 8/1, pp. 205-233 https://cran.r-project.org/web/packages/mclust/vignettes/mclust.html
